%Copyright (C) 2011 Julio Hernández <jhernandezgar@gmail.com>

%Permission is hereby granted, free of charge, to any person obtaining a copy
%of this software and associated documentation files (the "Software"), to deal
%in the Software without restriction, including without limitation the rights
%to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%copies of the Software, and to permit persons to whom the Software is
%furnished to do so, subject to the following conditions:

%The above copyright notice and this permission notice shall be included in
%all copies or substantial portions of the Software.

%THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%THE SOFTWARE.



\documentclass[11pt,a4paper]{moderncv}

% Temas de Moderncv
\moderncvtheme[blue]{casual}                
%Se pueden usar opcionalmente los siguientes colores 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
% Tema Clasico
%\moderncvtheme[green]{classic}                

% Codificacion
\usepackage[utf8]{inputenc}                   
\usepackage[T1]{fontenc}
\usepackage{lmodern} 
\usepackage{graphicx}
\usepackage{marvosym}

% Ajustar margenes de la pagina
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% Informacion Personal
\firstname{\huge Julio Cesar}
\familyname{\huge Hernández García}
\title{Resume - Julio Cesar Hernández García}
\address{Urb. Campo Alegre, Calle la Arboleda Casa Nº37, Carvajal, Edo. Trujillo, Venezuela}
\mobile{+584262799921}
\phone{+582712444854} 
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{jhernandezgar@gmail.com}                      % optional, remove the line if not wanted
\homepage{www.julioh.com.ve}                % optional, remove the line if not wanted
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt]{}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
\quote{Resume }                 % optional, remove the line if not wanted
%\quote{Any intelligent fool can make things bigger, more complex, and more violent. It takes a touch of genius -- and a lot of courage -- to move in the opposite direction.}% also optional

%\renewcommand{\listsymbol}{{\fontencoding{U}\fontfamily{ding}\selectfont\tiny\symbol{'102}}} % define another symbol to be used in front of the list items

% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}

% slanted small caps (only with roman family; the sans serif font doesn't exists :-()
%\usepackage{slantsc}
%\DeclareFontFamily{T1}{myfont}{}
%\DeclareFontShape{T1}{myfont}{m}{scsl}{ <-> cork-lmssqbo8}{}
%\usefont{T1}{myfont}{m}{scsl}Testing the font

% command and color used in this document, independently from moderncv 
\definecolor{see}{rgb}{0.5,0.5,0.5}% for web links
\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}% for text subscripts
% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
\begin{document}
\maketitle
%\makequote
\section{Objetive}
\cventry{Seeking a position as a System Administrator and a productive team member with a progressive company that provides opportunity for career growth and job satisfaction.}

\section{Skills}
\cventry{Strong communication and organizational skills, creativity, flexibility, reliability, a talent for team working, high emotional intelligence, social competencies and strong motivation for professional achievement, self-knowledge, and ability to handle conflict. Excellent abilities with web applications, Networks, software and hardware operation and maintenance.}
\cventry{Strong knowledge and experience with Linux, Solaris and Windows.}
\cventry{Strong knowledge of Internet Technologies such as TCP/IP, DNS, Memcached, Proxy servers, Reverse-proxy servers, Load Balancing, HTTP, LDAP.}
\cventry{Experience supporting and deploying highly scalable applications written in HTML, CSS, Javascript, C, Perl, PHP, Python, Coldfusion, Java with Oracle and MySQL databases.}
\cventry{Solid knowledge and experience of web servers such as Apache and lighttpd}
\cventry{Experience with automation and monitoring tools such as Puppet, Nagios, SNMP, Kickstart.}
\cventry{Experience with packaging RPMs and the SVN version control system.}
\cventry{Fluent in Spanish and English. Basic Portuguese and Dutch.}

\section{Education}
\cventry{2008--2012}{Management Specialist Science and Technology}{Universidad Rafael Belloso Chacin}{}{}{}
\cventry{2002--2008}{Computer Engineer}{Universidad Valle del Momboy}{}{}{}

\section{Additional Training}
\cventry{2010}{English Instrumental}{Universidad Valle del Momboy}{48 Hours}{made between 01/06 y 30/07/2010}{}
\cventry{2010}{Cisco Networking Academy: Routing Protocols and Concepts}{Universidad Valle del Momboy}{60 Hours}{made between 01/03 y 30/06/2010}{}
\cventry{2010}{Cisco Networking Academy: Networking Fundamentals}{Universidad Valle del Momboy}{60 Hours}{made between 04/01 y 19/02/2010}{}
\cventry{2008}{UML Design Workshop}{Biosoft C.A.}{32 Hours}{made between 30/08 y 03/08/2008}{}
\cventry{2007}{Introduction to the Exploration and Production}{Schulmberger}{16 Hours}{made between 01/07 y 02/07/2007}{}
\cventry{2006}{Wireless Telecommunications}{Cantv}{60 Hours}{made between 02/05 y 02/07/2006}{}
\cventry{2006}{Certified in Open Source}{Universidad Valle del Momboy}{192 Hours}{made between 02/05 y 02/07/2006}{}
\cventry{2003}{Component of English Academic}{Universidad Valle del Momboy - VEN-USA}{253 Hours}{made between 01/04 y 14/10/2003}{}
\cventry{2003}{Equipment Repair and Maintenance}{Universidad Valle del Momboy}{8 Hours}{made between el 11/04/2003}{}

\closesection{}
\pagebreak{}
\section{Work Experience}
\cventry{2011-2012}{Systems Analyst and Programmer}{IUTEMBI - Instituto Universitario de Tecnología Mario Briceño Iragorry}{Development of the website, as well as virtual classroom management and other subsystems have.}{}{}.\hfill{\itshape\color{see}\footnotesize{}Actual Trabajo}
\cventry{2009-2011}{Systems and Platform Manager}{Universidad Valle del Momboy}{Software Development, Server and Network Management}{}{}.\hfill{\itshape\color{see}\footnotesize{}}
\cventry{2007-2009}{Analyst and Technical Support}{Petróleos de Venezuela S.A }{}{}{Development and testing of software modules, on-site Technical Support}
\cventry{2006-2007}{Thesis}{C.V.G. Electrificación del Caroní C.A. }{}{}{Design and specifications Proprietary Platform Migration towards Free Software, SCADA at the substations of CVG Electrification of the Caroni, CA}
\cventry{2006}{Intern}{C.V.G. Electrificación del Caroní C.A.}{}{}{Web Development (PHP,MySQL), modules for providers, staff and Induction Guide Plant Division Caruachi.}
\cventry{2004-2006}{Scholar in Computer Lab}{Universidad Valle del Momboy}{}{}{Maintenance, Support, Networking, Administration Servers (Proxy, DNS, WEB, Mail, FTP) in Centos Linux.}

\section{Idiomas}
\cvlanguage{Spanish}{Native}{}
\cvlanguage{English}{Average}{}

\closesection{}
\pagebreak{}

\section{Presentation at Conferences and Meetings}
\cventry{2010}{Speaker}{FLISOL(Latin American Festival of Free Software)}{SlTrujillo, UNESR, Fundacite Trujillo}{\textit{Servers LAMP(Linux,Apache,Mysql,Php)}}{Valera,Trujillo - Venezuela}
\cventry{2010}{Workshop Facilitator}{X Congress ExpocTecnologia}{Universidad Valle del Momboy}{\textit{Servers LAMP(Linux,Apache,Mysql,Php}}{Valera,Trujillo - Venezuela}
\cventry{2007}{Speaker}{3th National Congress of Free Software-Trujillo}{GNU/Linux Organizado en Venezuela}{\textit{CMS: under free software}}{Valera,Trujillo - Venezuela}
\cventry{2007}{Speaker}{3th National Congress of Free Software-Monagas}{GNU/Linux Organizado en Venezuela}{\textit{SCADA's: under free software}}{Maturin,Monagas - Venezuela}
\cventry{2007}{Speaker}{3th National Congress of Free Software-Sucre}{GNU/Linux Organizado en Venezuela}{\textit{SCADA's: under free software}}{Cumana,Sucre - Venezuela}\cventry{2007}{Speaker}{3er Congreso Nacional de Software Libre-Anzoategui}{GNU/Linux Organizado en Venezuela}{\textit{SCADA's: Bajo Software Libre}}{Puerto la Cruz,Anzoategui - Venezuela}
\cventry{2007}{Speaker}{III International Workshop on Free Software}{Informatica 2007}{\textit{CMS: under free software}}{La Habana - Cuba}
\cventry{2006}{Speaker}{IV World Forum on Free Knowledge}{SOLVE(Software Libre Venezuela)}{\textit{CMS: under free software}}{Maturin,Monagas - Venezuela}
\cventry{2006}{Speaker}{Day of Free Software Installation}{Universidad Valle del Momboy}{\textit{How to Install Linux on Your Computer?}}{Valera,Trujillo - Venezuela}

\section{Events and Tutorials}
\cventry{2007}{Assistant}{Event}{Informatica 2007}{\textit{XII Convencion y Expo Internacional}}{La Habana - Cuba}
\cventry{2007}{Assistant}{Event}{Universidad Centroccidental Lisandro Alvarado}{\textit{Jornadas Universitarias de Software Libre}}{Lara - Venezuelaerú}
\cventry{2006}{Assistant}{Event}{Universidad Valle del Momboy}{\textit{VI Congreso de Expotecnologia}}{Trujillo - Venezuela}
\cventry{2005}{Assistant}{Event}{SOLVE(Software Libre Venezuela)}{\textit{3er Foro Mundial de Conocimiento Libre}}{Zulia - Venezuela}
\cventry{2005}{Assistant}{Event}{UNPLUG(Grupo de Usuario de Linux)}{\textit{1er Congreso Nacional de Software Libre}}{Trujillo - Venezuela}
\cventry{2005}{Assistant}{Event}{Universidad Valle del Momboy}{\textit{Auditoria de Sistemas}}{Trujillo - Venezuela}
\cventry{2004}{Assistant}{Event}{Universidad Valle del Momboy}{\textit{IV Congreso de Expotecnologia}}{Trujillo - Venezuela}
\cventry{2003}{Assistant}{Event}{Universidad Valle del Momboy}{\textit{VI Jornadas de Desarrollo Humano Sustentable}}{Trujillo - Venezuela}
\cventry{2003}{Assistant}{Event}{Universidad Valle del Momboy}{\textit{III Congreso de Expotecnologia}}{Trujillo - Venezuela}
\cventry{2003}{Assistant}{Event}{Universidad Valle del Momboy}{\textit{III Congreso de Expotecnologia}}{Trujillo - Venezuela}
\cventry{2002}{Assistant}{Event}{Gerenplanif}{\textit{I Congreso Binacional}}{Merida - Venezuela}
\cventry{2002}{Assistant}{Event}{Universidad Valle del Momboy}{\textit{V Jornadas de Desarrollo Humano Sustentable}}{Trujillo - Venezuela}
\cventry{2002}{Assistant}{Event}{Universidad Valle del Momboy}{\textit{I Jornadas Tecnologicas en Gestion Municipal}}{Trujillo - Venezuela}
\cventry{2002}{Assistant}{Event}{Universidad Centroccidental Lisandro Alvarado}{\textit{XI Jornadas Infociencias}}{Lara - Venezuel}

\closesection{}
\pagebreak{}

\section{Conocimientos}
\cvcomputer{SO}{Gnu/Linux (Debian,Ubuntu, Mandriva, Suse,Fedora, Red Hat), Windows(98, XP y Vista), MS-DOS BSD(OpenBSD,FreeBSD,Pfsense,MoNoWall)}{Admin.}{Web, Proxy, DNS,FTP y Correo.}
\cvcomputer{Ofimática}{Microsoft Office (Word, PowerPoint, Excel, Access) y OpenOffice.}{Hardware}{Ensamble de Equipos, Diagnostico de Fallas, Mantenimiento Preventivo del Computador.}
\cvcomputer{Programación estructurada y OO}{Java, J2ME, ASP.NET, Visual Basic.NET, Python,Perl,C/C++ (y librerías GTK,QT, PVM, MPI, OpenMP) y COBOL.}{Utilidades}{Eclipse,Geany,Vim,Nano,Gedit, Kile, TexnicCenter, Protégé.}
\cvcomputer{Programación Científica}{Matlab básico.}{Maquetación}{\LaTeX,Docbook}
\cvcomputer{Programación I.A.}{CLIPS, Scheme, Prolog.}{Scripting}{Bash Scripting, C-Shell, PHP Avanzado.}
\cvcomputer{Diseño Web}{HTML, XML, XSLT, XQuery, XPath, CSS.}{Base de datos}{MySQL, PostgreSQL, Oracle, SQLserver.}

\end{document}
